Understanding the impact of electronically-delivered parenting advice

### 2019-04-29 paper/cogsci2019/cogsci2019.Rmd
writing results

## Procedure.
After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the activity they had viewed. 
The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
In the Control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their child-directed speech. 
After three minutes of play had elapsed, parents were told they could stop playing and cameras and audio were turned off.
Parents were then asked to complete the PAQ before being debriefed.

@@

# Results

@@

## Lexical Diversity

@@

## Joint Attention

@@

In summary, while the number of tokens and types were higher in the experimental condition, lexical diversity (Type/Token ratio) was higher in the control condition. 
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

@@

Experiment 1 found that compared to parents who played with children as they normally would, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
Parents who watched a video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.

@@

## Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# Predicting lexical diversity based on experimental condition. 
modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.01

@@

We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8.7) = 3.06, *p*=.01).
There was no significant effect of age.
A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.

@@

## Joint Attention
```{r, e2ja-regressions, echo=F, include=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
e2ja = d

@@

@@

Similar to results in Experiment 1, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
There was a marginal effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of coordinated joint attention.
There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
However, there was a main effect of age on number of episodes of passive joint attention, duration of passive and coordinated joint attention, 
with the older children having fewer episodes of passive joint attention, shorter duration of passive joint attention, and longer duration of coordinated joint attention. 
These results suggest that children become more socially engaging in interactions with their caregivers as they develop.

## Two-column images

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

>>>>

### Procedure.
After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the activity the parent had viewed. 
The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
In the Control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless microphone (Shurre lavalier microphone) to record their child-directed speech. 
After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
Parents were then asked to complete the EPAQ before being debriefed.

@@

## Results

@@

### Lexical Diversity

@@

### Joint Attention

@@

In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
Demographics and EPAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

@@

Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)). 
We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.

@@

### Lexical Diversity
```{r, e2-lexdiv-regressions, echo=F, include=F}
# Predicting lexical diversity based on experimental condition. 
modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.01

@@

We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8.7) = 3.06, *p*=.01).
There was no significant effect of age.
A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
Figure X shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.

@@

### Joint Attention
```{r, e2ja-regressions, echo=F, include=F}
load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
e2ja = d

@@

There was a marginal effect of condition on total bids for joint attention. Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
There was no effect of condition on the number of episodes of passive or coordinated JA, nor on the duration of these episodes. 
For passive joint attention, there was a main effect of age on both the number and duration of episodes, with older children having fewer episodes of passive JA and episodes of shorter duration.
Moreover, older children had longer duration episodes of coordinated JA.
These results suggest that as children age, they become more socially engaged in interactions with their caregivers.

@@

In both experiments, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.

# Acknowledgements

This work was supported by a gift from Kinedu, Inc. 
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

### 2019-04-29 paper/cogsci2019/cogsci2019.tex
writing results

\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}

@@

\begin{abstract}
Early parenting practices play an important role in shaping the future
outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
particular, high-quality early interactions and language input appear to
facilitate language learning and result in higher levels of school
performance. The rise of phone- and tablet-based parenting applications
(``apps'') holds the promise of delivering low-cost, positive
interventions on parenting style to a variety of different populations.
Of special interest are the parents of very young children, who are
often difficult to reach in other ways. Yet little is known about the
effects of communicating to parents through app-based interventions. In
a study of one commercial app offering a collection of age-appropriate
activity videos, we find that the quality of parent-child interactions
increases in some ways as a result of using the app. Specifically, the
lexical diversity of parents' child-directed speech increases, and
measures of joint attention show\ldots{}

@@

Young children spend a large portion of their waking time at play,
variously manipulating objects, exploring their environment, and
interacting with caregivers and peers. Playing with objects allows them
to discover hidden object properties and relations, and to build a
causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
2007). Meanwhile, play also gives children an opportunity to set and
achieve goals (e.g., build a tower) and to practice a wide range of
motor skills (e.g., stacking) that will help them navigate the world
(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
learn about human relationships, both through imitation of adult
behaviors and by experiencing and learning to process emotional events
such as failures (Singer et al., 2006). Of course, young children are
rarely playing in isolation: caregivers often provide encouragement and
guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
Ross, 1976). Indeed, parenting practices early in childhood have been
shown to play an important role in shaping the future outcomes of young
children (Hart \& Risley, 1995; Heckman, 2006). While interventions
often have trouble reaching many parents of very young children, the
proliferation of mobile devices offers a good avenut for the digital
delivery of parenting advice (Breitenstein, Gross, \& Christophersen,
2014). However, the efficacy of digital parenting advice has not been
widely proven.

@@

Thus, including guided play in parenting practices early on is crucial
and will help with children's later performances in academic and social
situations. To intervene in parenting practices, Suskind and others did
a parent-directed home-visiting intervention experiment in 2015 for
children of low socioeconomic status. They showed that parents in
experimental group have greater knowledge of language development and
this effect sustained four months after the intervention. However,
although a number of interactive measures increased during the
experiment, including the number of word tokens, conversational turns,
and child vocalizations, these increases did not sustain after the
intervention (D. L. Suskind et al., 2015). That changes did not sustain
could be due to the intervention itself, or could merely be that the
methods of home-visiting is not sustainable enough for parents to easily
and constantly get parenting advice. Thus, new methods of delivering
parenting advice should be considered.

@@

With the widespread use of smartphones and tablets worldwide,
digitally-delivered interventions could address many of the logistical
barriers that have limited scaling up face-to-face delivery methods. A
review of 11 studies verified that digital delivery is a promising means
of effectively distributing interventions (Breitenstein et al., 2014).
However, the parent and child outcomes assessed in the review
(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
did not address the nature or quality of parent-infant interactions at a
detailed level, like if the interventions lead to children paying more
attention, or vocabulary changes in parents' language usages. Although
digitally-delivered ac-tivities are designed to promote learning and
cognitive development, it is unclear how they might affect these
dimensions of parent-child interactions. Thus, we want to conduct this
experiment to explore if and how digital scaffolding of activities
affect the social and linguistic characteristics of parent-child
ineractions. The quality of parent-child interactions can be measured by
both the social engagement of parents (e.g., joint attention to objects
in the environment)(Bigelow, MacLean, \& Proctor, 2004) and the quality
of language (e.g., vocabulary diversity) (Malvern, Richards, Chipere, \&
Durán, 2004).

@@

60 infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20
12-17.9 month-olds, and 20 18-24 month-olds) and their parents
participated in a museum in northern California. We included infants who
were exposed to English at least 50 percent of the time (n = 58) or who
were exposed less but whose participating parent reported that they
primarily speak English with their child at home (n = 2). 61\% of
participants (n = 37) had been exposed to two or more languages as
indicated by their parent. Parents identified their children as White (n
= 25), Asian (n = 11), African American/Black (n = 2), Biracial (n =
12), other (n = 5), or declined to state (n = 5). Fifteen parents
reported their child was of Hispanic origin. Parents tended to be
highly-educated, with reports of highest level of education ranging from
completed high school (n = 5), some college (n = 6), four-year college
(n = 14), some graduate school (n = 1), to completed graduate school (n
= 28) or declined to state (n = 6).

@@

Stimuli included videos from the Kinedu (Kinedu Inc.) commercial
parenting application. The videos were designed to show activities to
parents that they could perform with their child in order to foster
cognitive and physical development, and were targeted to the child's age
and level of development. In each video, an adult and child perform the
activity while a narrator explains the activity and its purpose. We
selected two videos for each of three age groups in our sample (6-11.9
months, 12-17.9 months, 18-23.94 months). More information about the
specific videos is available in the Appendix. Participants were also
given a set of props corresponding to those in the video they watched so
that they could complete the activity. The props associated with each
video are listed in the Appendix.

Participants were randomly assigned to either the \emph{Video} condition
or the \emph{Control} condition. Participating parents in the Video
condition were assigned to watch one of the two activity videos
available for their child's age group. Participating parents in the
Control condition watched no activity video, and were merely asked to
play with their child as they normally would. The Control condition was
yoked to the Activity Video condition such that for every participant in
the Video condition who saw a particular video and received the
associated props, a participant in the Control condition received the
same props but did not watch the activity video. Parents also completed
the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
attitudes about parenting and child development along three dimensions:
rules and respect, early learning, and affection and attachment.

@@

We fit a mixed-effects linear regression predicting TTR as a function of
condition, age (scaled and 0-centered), gender, and parent's education
level with a random intercept per video using lme4 (Bates, Mächler,
Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
condition (mean: 0.32) than in the Control condition (mean: 0.43,
\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
significant effects of age, gender, or parent's level of education. A
similar mixed-effects linear regression instead predicting MTLD also
found significantly lower lexical diversity in the Video condition
(mean: 15.7) than in the Control condition (mean: 21.9,
\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
significant effects. Figure 1 shows the mean of each lexical diversity
measure (TTR and MTLD) by condition.

@@

@@

We fit a mixed-effects linear regression predicting TTR and MTLD as a
function of age (scaled and 0-centered) and condition with a random
intercept per video using lme4 (Bates et al., 2015). There was
significantly lower TTR in the Video condition (mean: 0.38) than in the
Control condition (mean: 0.47, \(\beta=-.09\), t(8.7) = 3.06,
\emph{p}=.01). There was no significant effect of age. A similar
mixed-effects linear regression instead predicting MTLD found no
significant effects of age or condition. Figure 1 shows the mean of each
lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the number of word
tokens and types, finding no significant effects of of age or condition.

@@

@@

@@

@@

>>>>

\author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\ {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}

@@

\begin{abstract}
Early parenting practices play an important role in shaping the future
outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
particular, high-quality early interactions and language input appear to
facilitate language learning and result in higher levels of school
performance. The rise of phone- and tablet-based parenting applications
(``apps'') holds the promise of delivering low-cost, positive
interventions on parenting style to a wide variety of populations. Of
special interest are the parents of very young children, who are often
difficult to reach in other ways. Yet little is known about the effects
of communicating to parents through app-based interventions. In a study
of one commercial app offering a collection of age-appropriate activity
videos, we find that the quality of parent-child interactions increases
in some ways as a result of using the app. Specifically, the lexical
diversity of parents' child-directed speech increases, and measures of
joint attention show\ldots{}

@@

Children of any given age show remarkable variability in their levels of
language proficiency (Fenson et al., 1994),

Young children spend a large portion of their waking time at play,
variously manipulating objects, exploring their environment, and
interacting with caregivers and peers. Playing with objects allows them
to discover hidden object properties and relations, and to build a
causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
2007). Meanwhile, play also gives children an opportunity to set and
achieve goals (e.g., build a tower) and to practice a wide range of
motor skills (e.g., stacking) that will help them navigate the world
(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
learn about human relationships, both through imitation of adult
behaviors and by experiencing and learning to process emotional events
such as failures (Singer et al., 2006). Of course, young children are
rarely playing in isolation: caregivers often provide encouragement and
guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
Ross, 1976). The quality of interactions during such guided play has
been shown to influence language learning: parents' joint attention to
objects that their child was focused on was positively correlated with
the child's subsequent vocabulary growth (M. Carpenter \& Tomasello,
1998; Tomasello \& Farrar, 1986). Episodes of joint attention during
guided play have also been found to contain more age-appropriate
advanced forms of play (Bigelow, MacLean, \& Proctor, 2004). More
generally, parenting practices early in childhood have been shown to
play an important role in shaping the future outcomes of young children
(Hart \& Risley, 1995; Heckman, 2006). While interventions often have
trouble reaching many parents of very young children, the proliferation
of mobile devices offers a good avenut for the digital delivery of
parenting advice (Breitenstein, Gross, \& Christophersen, 2014).
However, the efficacy of digital parenting advice has not been widely
proven.

@@

Thus, including guided play in parenting practices from an early age may
boost children's language and educational outcomes. A recent home-visit
parenting practices intervention targeting children of low socioeconomic
status found that parents in the intervention group gained knowledge of
language development, and that this effect sustained four months after
the intervention (D. L. Suskind et al., 2015). However, although a
number of interactive measures increased during the experiment,
including the number of word tokens, conversational turns, and child
vocalizations, these increases did not sustain after the intervention.
That changes did not sustain could be due to the intervention itself, or
could merely be that the methods of home-visiting is not sustainable
enough for parents to easily and constantly get parenting advice. Thus,
new methods of delivering parenting advice should be considered.

@@

With the widespread use of smartphones and tablets worldwide,
digitally-delivered interventions could address many of the logistical
barriers that have limited scaling up face-to-face delivery methods. A
review of 11 studies verified that digital delivery is a promising means
of effectively distributing interventions (Breitenstein et al., 2014).
However, the parent and child outcomes assessed in the review
(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
did not address the nature or quality of parent-infant interactions at a
detailed level, like if the interventions lead to children paying more
attention, or vocabulary changes in parents' language usages. Although
digitally-delivered ac-tivities are designed to promote learning and
cognitive development, it is unclear how they might affect these
dimensions of parent-child interactions. Thus, we want to conduct this
experiment to explore if and how digital scaffolding of activities
affect the social and linguistic characteristics of parent-child
ineractions. The quality of parent-child interactions can be measured by
both the social engagement of parents (e.g., joint attention to objects
in the environment)(Bigelow et al., 2004) and the quality of language
(e.g., vocabulary diversity) (Malvern, Richards, Chipere, \& Durán,
2004).

@@

60 infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20
12-17.9 month-olds, and 20 18-24 month-olds) and their parents
participated in a museum in northern California. We included infants who
were exposed to English at least 50 percent of the time (n = 58) or who
were exposed less but whose participating parent reported that they
primarily speak English with their child at home (n = 2). 61\% of
participants (n = 37) had been exposed to two or more languages as
indicated by their parent. Parents identified their children as White (n
= 25), Asian (n = 11), African American/Black (n = 2), Biracial (n =
12), other (n = 5), or declined to state (n = 5). Fifteen parents
reported that their child was of Hispanic origin. Parents tended to be
highly-educated, with reports of highest level of education ranging from
completed high school (n = 5), some college (n = 6), four-year college
(n = 14), some graduate school (n = 1), to completed graduate school (n
= 28) or declined to state (n = 6).

@@

Stimuli included videos from the Kinedu (Kinedu Inc.) commercial
parenting application. The videos were designed to show activities to
parents that they could perform with their child in order to foster
cognitive and physical development, and were targeted to the child's age
and level of development. In each video, an adult and child perform the
activity while a narrator explains the activity and its purpose. We
selected two videos for each of three age groups in our sample (6-11.9
months, 12-17.9 months, 18-23.94 months). More information about the
specific videos is available in the Appendix. Participants were also
given a set of toys corresponding to those in the video that they
watched so that they could complete the activity. The toys associated
with each video are listed in the Appendix.

Participants were randomly assigned to either the \emph{Video} condition
or the \emph{Control} condition. Parents participating in the Video
condition were assigned to watch one of the two activity videos
available for their child's age group, while parents in the Control
condition watched no activity video, and were simply asked to play with
their child as they normally would. The Control condition was yoked to
the Activity Video condition such that for every participant in the
Video condition who saw a particular video and received the associated
props, a participant in the Control condition received the same props
but did not watch the activity video. Parents also completed the Early
Parenting Attitudes Questionnaire (EPAQ; (Hembacher \& Frank, 2018)).
The EPAQ measures parents' attitudes about parenting and child
development along three dimensions: rules and respect, early learning,
and affection and attachment.

@@

We fit a mixed-effects linear regression predicting TTR as a function of
condition, age (scaled and 0-centered), gender, and parent's education
level with a random intercept per video using lme4 (D. Bates, Mächler,
Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
condition (mean: 0.32) than in the Control condition (mean: 0.43,
\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
significant effects of age, gender, or parent's level of education. A
similar mixed-effects linear regression instead predicting MTLD also
found significantly lower lexical diversity in the Video condition
(mean: 15.7) than in the Control condition (mean: 21.9,
\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
significant effects. Figure 1 shows the mean of each lexical diversity
measure (TTR and MTLD) by condition.

@@

We fit a mixed-effects linear regression predicting the number of bids
for joint attention (JA) as a function of fixed effects of condition,
age (scaled and 0-centered), gender, parent's education level, and the
subscales of the EPAQ: Early Learning (EL), Affection and Attachment
(AA), and Rules and Respect (RR), along with interactions of condition
and EL, AA, and RR. This lme4 model included random intercepts per
video. There were significantly more bids for JA in the Video condition
(mean: X) than in the Control condition (mean: X, \(\beta=3.51\),
t(40.3) = 2.95, \emph{p}\textless{}.01). There were no other significant
effects. Mixed-effects regressions with the same structure were
performed predicting the number of episodes of coordinated and passive
JA, and the total duration of time spent in coordinated and passive JA.
There were no significant effects on the number or total duration of
coordinated JA episodes, nor on the total duration of passive JA
episodes. For the regression predicting the number of passive joint
attention episodes, the only significant effect was an interaction of
condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
\emph{p}\textless{}.05), showing that\ldots{} Figure X shows \ldots{} by
condition.

@@

We fit a mixed-effects linear regression predicting TTR and MTLD as a
function of age (scaled and 0-centered) and condition with an
interaction term, and with random intercepts per video using lme4 (D.
Bates et al., 2015). There was significantly lower TTR in the Video
condition (mean: 0.38) than in the Control condition (mean: 0.47,
\(\beta=-.09\), t(8.7) = 3.06, \emph{p}=.01). There was no significant
effect of age. A similar mixed-effects linear regression instead
predicting MTLD found no significant effects of age or condition. Figure
1 shows the mean of each lexical diversity measure (TTR and MTLD) by
condition. Regressions with the same structure predicting the number of
word tokens and types found no significant effects of age or condition.

@@

\hypertarget{ref-Fenson1994}{}
Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
communicative development. \emph{Monographs of the Society for Research
in Child Development}, i--185.

@@

\hypertarget{ref-Hembacher2018}{}
Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes
questionnaire: Measuring intuitive theories of parenting and child
development. \emph{PsyArXiv}. \url{http://doi.org/10.31234/osf.io/hxk3d}

@@

\hypertarget{ref-Carpenter1998}{}
M. Carpenter, K. Nagell, \& Tomasello, M. (1998). Social cognition,
joint attention, and communicative competence from 9 to 15 months of
age. \emph{Monographs of the Society for Research in Child Development},
\emph{63}(4), i--vi, 1--143.

@@

\hypertarget{ref-Tomasello1986}{}
Tomasello, M., \& Farrar, M. J. (1986). Joint attention and early
language. \emph{Child Development}, \emph{57}(6), 1454--1463.
